---
title: "p8105_hw5_LG2982"
author: "Lizbeth Gomez"
date: "11/8/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Problem 1:

#### Data Import
```{r}
library(tidyverse)
library(purrr)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```
There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement

#### Function and Replacement
```{r, Problem 1}



output <- vector("list", length = ncol(iris_with_missing))

na_replace <- function(x) {
  if (is.numeric(x)) {
    replace_na(x, mean(x, na.rm = TRUE))
    
  }  else if (is.character(x)) {
    replace_na(x, "virginica")
  }
}

output = map(iris_with_missing, na_replace)


```

## Problem 2:
#### Data Import
Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
- Start with a dataframe containing all file names; the list.files function will help
- Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

```{r, Problem 2}

file_names_df = tibble(
  file_names = list.files(path = "./data/Problem_1"))



read_data <- function(file_name) {
  
  read_csv(paste0("data/Problem_1/", file_name))
  
}


study_data_import = 
  file_names_df %>% 
  mutate(
    study_data = map(file_names_df[[1]], read_data))
```
#### Data Tidy
- Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
study_data_tidy = 
  study_data_import %>% 
  unnest() %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  separate(file_names, into = c("study_arm", "subject_id"), sep = "\\_") %>% 
  mutate(
    subject_id = str_replace(subject_id, "\\.csv", ""),
    subject_id = str_remove(subject_id, "^0+"), 
    week = str_replace(week, "\\week_", ""), 
    study_arm = recode(study_arm, con = "Control", exp = "Experimental")) 

study_data_tidy
```

#### Plot of participants' observation over time

Make a spaghetti plot showing observations on each subject over time, and comment on differences between group

```{r}
study_data_tidy %>% 
  ggplot(aes(x = week, y = observation, color = subject_id, group = subject_id)) + 
  geom_line() +
  facet_grid(~study_arm) +
  labs(
    title = "Observations Over 8 Weeks", 
    x = "Week", 
    y = "Observation", 
    color = "Participant") + 
  viridis::scale_color_viridis(discrete = TRUE)

```
Comments: As shown by the graphs, the experimental arm in general has a higher number of observation than the control. 


## Problem 3:


```{r, Problem 3}

sim_regression = function(n, beta0 = 2,  beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

```

```{r}
sim_regression(n =30)
```

